Notes on Etling velocity profile for Ekman/Prandtl layer

### 2024-11-21 cover_letter/20241114_coverletter.tex
ready to submit (?)

\betreff{Submission of our manuscripts ``Wind veer and speed in turbulent Ekman flow Part I and II'' }

@@

We are pleased to submit two connected research papers on a topic of crucial importance for Boundary-Layer Meteorology,
namely the profiles on wind speed and direction in the lower part of the boundary layer.
%
The research papers are entitled
\begin{itemize}
\item[I] Wind veer and speed in turbulent Ekman flow Part I: Scaling Analysis and universal profile model
\item[II] Wind veer and speed in turbulent Ekman flow Part II: Extrapolation to Atmospheric Scale Separation
\end{itemize}

>>>>

\betreff{Submission of our two-part manuscript ``Wind veer and speed in turbulent Ekman flow" }

@@

We are pleased to submit two connected research papers on a central topic in Boundary-Layer Meteorology,
namely the profiles on wind speed and direction in the lower part of the boundary layer.
%
The research papers are entitled
\begin{itemize}
\item[I] Wind veer and speed in turbulent Ekman flow part I: scaling analysis and universal profile model
\item[II] Wind veer and speed in turbulent Ekman flow part II: extrapolation to atmospheric scale separation
\end{itemize}
